 

### 2023-02-03 markdown/methods.Rmd
literature recherche

Write your methods here. In this tutorial you can use this already made file\\to add examples of figures and tables and explore knitr and kableExtra functionalities!

>>>>

# Materials and Methods

## Materials

For analysis two types of cells were used. One type is the Jurkat-based cell line (J-lat) with integrated HIV.

The other type of cells are macrophages with a sample size of 72 cells. The analysis is done with two groups. A HIV negative (HIV-) control group and a HIV positive (HIV+) group.

## Data

### Acquisition

Analysis of the data was done with MaxQuant \citep{Cox2008}
